# Part 6: Prediction
```{r retrain}
bestModels <<- bmaBest(yX = yX)
save(bestModels, file = "./analysis/bestModels.Rdata")
```


```{r prediction}
cases <- read.csv(file = "../inst/extdata/movies2predict.csv", stringsAsFactors = FALSE)
p <- rbindlist(lapply(bestModels, function(m) {
  p <- predict(object = m, estimator = "MPM", newdata = cases)
  e <- cv.summary.bas(pred = p$fit, ytrue = as.numeric(cases$audience_score))
  p$fit <- c(p$fit,e)
  as.list(round(as.numeric(p$fit), 1))
}))
predictions <- t(as.data.frame(p, rownames = FALSE))
colnames(predictions) <- names(bestModels)
predictions <- cbind("Film" = c(cases$title, "MSE"), predictions, `Audience Score` = c(cases$audience_score, ""))
rownames(predictions) <- NULL
```

Five films from 2016 were selected from the BoxOfficeMojo.com, IMDb, and Rotten Tomatoes websites and predictions were rendered using the four models from the model evaluation section:  
* Akaike Information Criterion (Median Prediction Model)   
* Zellner's g-prior (Median Predictive Model)   
* Empirical Bayes-Global (Median Predictive Model)   
* Hyper-g Laplace (Median Predictive Model)   

## Predictions
The predictions, true values, and mean squared errors are summarized for each movie and model in `r kfigr::figr(label = "results", prefix = TRUE, link = TRUE, type="Table")`.

`r kfigr::figr(label = "results", prefix = TRUE, link = TRUE, type="Table")`: Prediction Results
```{r results}
knitr::kable(predictions, digits = 1) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```


```{r ci}
graphics::par(mfrow = c(2,2), family = "Open Sans")
lapply(bestModels, function(m) {
  p <- predict(object = m, estimator = "MPM", newdata = cases, se.fit = TRUE)
  ci <- confint(p, parm = "pred")
  print(plot(ci, main = m$prior))
})
```
* * *
