---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Appendix
## Appendix A: Model Analyses
### `r models[[1]]$priorDesc`
#### Model Space: `r models[[1]]$priorDesc`
```{r a_model_space_1}
par(cex.axis = 2, cex.lab = 2, cex.sub = 2, cex.main = 2, mar = c(5,15,4,2) + 0.1)
image(models[[1]], rotate = F, cex = 2)
```
`r kfigr::figr(label = "model_space_1", prefix = TRUE, link = TRUE, type="Figure")`: Model space `r models[[1]]$priorDesc`

#### Model Analysis: `r models[[1]]$priorDesc`
```{r a_BIC_analysis, fig.height=15}
par(mfrow = c(2,2), cex.axis = 2, cex.lab = 2, cex.sub = 2, cex.main = 2, mar = c(10,5,4,2) + 0.1)
plot(models[[1]], ask = F)
```
`r kfigr::figr(label = "a_rvf1", prefix = TRUE, link = TRUE, type="Figure")`: Residuals vs Fitted `r models[[1]]$priorDesc`

#### Parameter Estimates: `r models[[1]]$priorDesc`

```{r a_pdc, fig.height=24}
p <- list()
p$BMA <- analysis$pdc[[1]]$BMA$plot
p$BPM <- analysis$pdc[[1]]$BPM$plot
p$HPM <- analysis$pdc[[1]]$HPM$plot
p$MPM <- analysis$pdc[[1]]$MPM$plot
n <- length(p)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(p, ncol=nCol))
```
`r kfigr::figr(label = "a_pdc", prefix = TRUE, link = TRUE, type="Figure")`: Posterior parameter estimates and credible intervals 
