# Appendix
## Appendix A: Functions Overview
`r kfigr::figr(label = "functions", prefix = TRUE, link = TRUE, type="Table")`: Package functions
```{r functions}
functions <- read.csv(file = "../vignettes/figs_tables/functions.csv")
functions <- functions %>% select(Function, Description)
knitr::kable(functions) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center") %>%
  kableExtra::group_rows("Data", 1,1) %>%
  kableExtra::group_rows("Exploratory Data Analysis", 2,9) %>%
  kableExtra::group_rows("Models", 10,23) %>%
  kableExtra::group_rows("Predictions", 24,24) %>%
  kableExtra::group_rows("All", 25,25)
```

The primary functions are outlined below. The complete source code is available at https://github.com/DataScienceSalon/Bayesian-Regression.

## Appendix B: Data Function (Preprocessing)
```{r a-preprocess, code=readLines('../R/preprocess.R')[4:51], echo=TRUE, eval=FALSE}
```
`r kfigr::figr(label = "a-preprocess", prefix = TRUE, link = TRUE, type="Code")`: Preprocessing function

## Appendix C: Bayesian Model Averaging
```{r a-bma, code=readLines('../R/bma.R')[4:123], echo=TRUE, eval=FALSE}
```
`r kfigr::figr(label = "a-bma", prefix = TRUE, link = TRUE, type="Code")`: Bayesian model averaging function

## Appendix D: Bayesian Prediction
```{r a-bmaPredict, code=readLines('../R/bmaPredict.R')[4:73], echo=TRUE, eval=FALSE}
```
`r kfigr::figr(label = "a-bmaPredict", prefix = TRUE, link = TRUE, type="Code")`: Bayesian prediction function